---
title: "MCL_MATCH_WES"
output: html_notebook
author: HA Hill
---

```{r}
library(tidyverse)
library(maftools)
library(gt)
```

#Filter out extraneous variants.

```{r}
wes_mcl <- MCL_mutations
```

```{r}
wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="Intron" & Hugo_Symbol != "Unknown")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="3'UTR")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="Silent")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="RNA")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="5'Flank")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="5'UTR")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="DE_NOVO_START_OUT_FRAME")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="DE_NOVO_START_IN_FRAME")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="In_Frame_Ins")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="In_Frame_Del")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="COULD_NOT_DETERMINE")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="START_CODON_SNP")

wes_mcl <- wes_mcl %>%
filter(Variant_Classification !="START_CODON_INS")

wes_mcl <- wes_mcl %>%
filter(Chromosome !="MT")

```

#Filter tumor vaf < 0.03

```{r}
wes_mcl_filter <- wes_mcl %>% 
filter(tumor_f > 0.03) 

wes_mcl_filter <- wes_mcl_filter %>% filter(!is.na(COSMIC_overlapping_mutations) | !is.na(CGC_Tumor_Types_Somatic) | !is.na(FamilialCancerDatabase_Syndromes) | !is.na(Achilles_Top_Genes) |!is.na(COSMIC_fusion_genes)|!is.na(CGC_Tumor_Types_Germline)|!is.na(DNARepairGenes_Activity_linked_to_OMIM)|!is.na(CGC_Translocation_Partner)|!is.na(GO_Molecular_Function)|(Hugo_Symbol=="NSD2")|(Hugo_Symbol=="KMT2A")|(Hugo_Symbol=="MAP3K14")|(Hugo_Symbol=="BTK")|(Hugo_Symbol=="IGH") | (Hugo_Symbol=="MYC")|(Hugo_Symbol=="TP53")|(Hugo_Symbol=="ATM")|(Hugo_Symbol=="TRAF2")|(Hugo_Symbol=="CHD2")|(Hugo_Symbol=="TLR2")|(Hugo_Symbol=="ARID2A")|(Hugo_Symbol=="RIMS2")|(Hugo_Symbol=="NOTCH2")|(Hugo_Symbol=="SPEN")|(Hugo_Symbol=="CARD11")|(Hugo_Symbol=="CCND1")|(Hugo_Symbol=="SP140")|(Hugo_Symbol=="CDKN2A")|(Hugo_Symbol=="S1PR1"))

wes_mcl_filter <- wes_mcl_filter %>% 
  filter(ClinVar_VCF_AF_EXAC < 0.001 | is.na (ClinVar_VCF_AF_EXAC))

```
