---
title: "Figure 1"
author: HA Hill
project: MCL MATCH
output:html_notebook

---
#Figure 1

#This heatmap depicts the enrichment scores (ES) from single sample gene-set variation analysis (GSVA) of 20 MCL patient samples. The enrichment scores are based on singular samples and do not represent differentially expressed pathways. 

##The custom MCL gene set (MCL MATCH Gene set) was constructed using information from the MSigDB Hallmark gene sets (https://www.gsea-msigdb.org/gsea/msigdb/collections.jsp) and the Tumor 360 gene panel by Nanostring. Additionally the CAR-T gene set was constructed as described in the manuscript.The pathways correspond to precision therapeutics which were assessed in patient derived cell-lines and PDX. 

```{r}
library(tidyverse)
library(GSVA)
library(pheatmap)
library(readxl)
library(RColorBrewer)
```

```{r}
#Import MCL MATCH gene set (Supplementary File 1, Table 2)
MATCH <- read_excel("Supp_File_1_Genesets.xlsx", sheet = "Matched_Therapy_Geneset")

MATCH <- sapply(MATCH, as.character)
MATCH[is.na(MATCH)] <- " "
MATCH <- as.data.frame(MATCH)
```

```{r}
#Import gene expression read counts from normalized and batch corrected Nanostring .rcc files ()

Counts <- read_delim("MCL_MATCH_normalizedCountsWithAnnotations.tsv", 
delim = "\t", escape_double = FALSE, 
trim_ws = TRUE)

MATCH <- Supp_File_1_Genesets
```

```{r}
#Create a matrix of gene counts

Counts_mat <- data.frame(Counts, row.names = Counts$Gene)

Counts <- Counts_mat %>% mutate(across(c(2:21), as.numeric))

rownames(Counts) <- Counts$Symbol

Counts_mat <- as.matrix(Counts[,-1])


#Run the GSVA algorithm to calculate patient level enrichment score for each gene

gsvaPar <- gsvaParam(Counts_mat, MATCH)

gsva.es <- gsva(gsvaPar, verbose=FALSE)

#One patient has 0 as an ES prompting R to put in NA

gsva.es[is.na(gsva.es)] <- 0
```

```{r}
set.seed(202)

#Utilize Pheatmap to create visualization of ES

p <- pheatmap(gsva.es, col = colorRampPalette(rev(brewer.pal(n = 7, name ="RdBu")))(100), legend=T, clustering_distance_cols = 'correlation', clustering_distance_rows = 'correlation', clustering_method="average", main = "GSVA Enrichment Scores using MCL MATCH Gene Sets")
```

```{r}
pdf("GSVA_MATCH_Figure1.pdf", height = 10, width = 8)
p
dev.off()
```

